proportion_of_importance_per_annotation

### 2019-07-12 Scripts/proportion_of_importance_per_annotation.Rmd
added 5kb results

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/all_annotations/gm12878")
annots <- gsub(paste(c("Gm12878-",".bed", 
                             "-Haib", 
                             "-Sydh",
                             "-Uta",
                             "-Uw",
                             "-Broad",
                             "-Uchicago"), collapse = "|"), "", annots)
annots <- annots[!duplicated(annots)]

chromstates <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
chromstates <- chromstates[grep("Gm12878", chromstates)]
chromstates <- gsub(paste0(c("Gm12878-", ".bed"), collapse = "|"),"",chromstates)

histones <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
histones <- histones[grep("Gm12878", histones)]
histones <- gsub(paste0(c("Gm12878-", ".bed"), collapse = "|"),"",histones)

tfbs <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878")
tfbs <- gsub(paste0(c("Gm12878-", ".bed", "-Haib", "-Sydh", "-Broad", "-Uw", "-Uta", "-Chicago"), collapse = "|"),"", tfbs)
tfbs <- tfbs[!duplicated(tfbs)]

@@

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars.rds"))
	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars.rds"))
	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars.rds"))
	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars.rds"))
	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

```{r}
all_propimp_gm12878 <- data.frame(Importance=c(varimp_gm12878_10kb$aveimp10kb,
                                                   varimp_gm12878_25kb$aveimp25kb,
                                                   varimp_gm12878_50kb$aveimp50kb,
                                                   varimp_gm12878_100kb$aveimp100kb),
                                  Feature=c(as.character(varimp_gm12878_10kb$Feature),
                                            as.character(varimp_gm12878_10kb$Feature),
                                            as.character(varimp_gm12878_10kb$Feature),
                                            as.character(varimp_gm12878_10kb$Feature)),
                                  Resolution=c(rep("10 kb", 107),
                                               rep("25 kb", 107),
                                               rep("50 kb", 107),
                                               rep("100 kb", 107))
                                  )

@@

all_propimp_gm12878_summ <- data.frame(Prop.VI = c(
                                                   #10kb
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="10 kb" & all_propimp_gm12878$Annotation=="CSS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="10 kb")]),
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="10 kb" & all_propimp_gm12878$Annotation=="HM")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="10 kb")]),
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="10 kb" & all_propimp_gm12878$Annotation=="TFBS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="10 kb")]),

@@

                                                   #100kb
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb" & all_propimp_gm12878$Annotation=="CSS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb")]),
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb" & all_propimp_gm12878$Annotation=="HM")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb")]),
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb" & all_propimp_gm12878$Annotation=="TFBS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb")])),
                                       Resolution = c(rep("10 kb", 3),
                                                      rep("25 kb", 3),
                                                      rep("50 kb", 3),
                                                      rep("100 kb", 3)),
                                       Annotation = rep(c("CSS","HM","TFBS"), 4))

all_propimp_gm12878_summ$Resolution <- factor(all_propimp_gm12878_summ$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))

@@

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/all_annotations/k562")
annots <- gsub(paste(c("K562-",".bed", 
                             "-Haib", 
                             "-Sydh",
                             "-Uta",
                             "-Uw",
                             "-Broad",
                             "-Uchicago"), collapse = "|"), "", annots)
annots <- annots[!duplicated(annots)]

chromstates <- list.files("Z:/TAD_data_analysis/annotations/BroadHMM")
chromstates <- chromstates[grep("K562", chromstates)]
chromstates <- gsub(paste0(c("K562-", ".bed"), collapse = "|"),"",chromstates)

histones <- list.files("Z:/TAD_data_analysis/annotations/HistoneModifications")
histones <- histones[grep("K562", histones)]
histones <- gsub(paste0(c("K562-", ".bed"), collapse = "|"),"",histones)

tfbs <- list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/K562")
tfbs <- gsub(paste0(c("K562-", ".bed", "-Haib", "-Sydh", "-Broad", "-Uw", "-Uta", "-Chicago"), collapse = "|"),"", tfbs)
tfbs <- tfbs[!duplicated(tfbs)]

@@

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars.rds"))
	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars.rds"))
	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars.rds"))
	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars.rds"))
	  varimps$Feature <- gsub(paste0(c("`","_dist"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

```{r}
all_propimp_K562 <- data.frame(Importance=c(varimp_K562_10kb$aveimp10kb,
                                                   varimp_K562_25kb$aveimp25kb,
                                                   varimp_K562_50kb$aveimp50kb,
                                                   varimp_K562_100kb$aveimp100kb),
                                  Feature=c(as.character(varimp_K562_10kb$Feature),
                                            as.character(varimp_K562_10kb$Feature),
                                            as.character(varimp_K562_10kb$Feature),
                                            as.character(varimp_K562_10kb$Feature)),
                                  Resolution=c(rep("10 kb", 141),
                                               rep("25 kb", 141),
                                               rep("50 kb", 141),
                                               rep("100 kb", 141))
                                  )

@@

all_propimp_K562_summ <- data.frame(Prop.VI = c(
                                                   #10kb
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="10 kb" & all_propimp_K562$Annotation=="CSS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="10 kb")]),
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="10 kb" & all_propimp_K562$Annotation=="HM")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="10 kb")]),
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="10 kb" & all_propimp_K562$Annotation=="TFBS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="10 kb")]),

@@

                                                   #100kb
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb" & all_propimp_K562$Annotation=="CSS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb")]),
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb" & all_propimp_K562$Annotation=="HM")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb")]),
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb" & all_propimp_K562$Annotation=="TFBS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb")])),
                                       Resolution = c(rep("10 kb", 3),
                                                      rep("25 kb", 3),
                                                      rep("50 kb", 3),
                                                      rep("100 kb", 3)),
                                       Annotation = rep(c("CSS","HM","TFBS"), 4))

all_propimp_K562_summ$Resolution <- factor(all_propimp_K562_summ$Resolution, levels=c("10 kb", "25 kb", "50 kb", "100 kb"))

>>>>

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878", pattern = "*.bed")
annots <- gsub(paste(c("Gm12878-",".bed", 
                             "-Haib", 
                             "-Sydh",
                             "-Uta",
                             "-Uw",
                             "-Broad",
                             "-Uchicago"), collapse = "|"), "", annots)
annots <- annots[!duplicated(annots)]

chromstates <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/BroadHMM")
chromstates <- chromstates[grep("Gm12878", chromstates)]
chromstates <- gsub(paste0(c("Gm12878-", ".bed"), collapse = "|"),"",chromstates)

histones <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/HistoneModifications")
histones <- histones[grep("Gm12878", histones)]
histones <- gsub(paste0(c("Gm12878-", ".bed"), collapse = "|"),"",histones)

tfbs <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/gm12878/TFBS")
tfbs <- gsub(paste0(c("Gm12878-", ".bed", "-Haib", "-Sydh", "-Broad", "-Uw", "-Uta", "-Chicago"), collapse = "|"),"", tfbs)
tfbs <- tfbs[!duplicated(tfbs)]

@@

##5kb

```{r}
varimp_gm12878_5kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_gm12878_5kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_noenet.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                           "_dist",
	                           "Gm12878-",".bed", 
                             "-Haib", 
                             "-Sydh",
                             "-Uta",
                             "-Uw",
                             "-Broad",
                             "-Uchicago"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_gm12878_5kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_gm12878_5kb <- data.frame(Feature = rownames(varimp_gm12878_5kb),
                                  aveimp5kb = rowMeans(varimp_gm12878_5kb, na.rm = TRUE),
                                  sdimp5kb = apply(varimp_gm12878_5kb,1, sd, na.rm = TRUE))
rownames(varimp_gm12878_5kb) <- NULL
```

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_noenet.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                           "_dist",
	                           "Gm12878-",".bed", 
                             "-Haib", 
                             "-Sydh",
                             "-Uta",
                             "-Uw",
                             "-Broad",
                             "-Uchicago"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_noenet.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                           "_dist",
	                           "Gm12878-",".bed", 
                             "-Haib", 
                             "-Sydh",
                             "-Uta",
                             "-Uw",
                             "-Broad",
                             "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_noenet.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                           "_dist",
	                           "Gm12878-",".bed", 
                             "-Haib", 
                             "-Sydh",
                             "-Uta",
                             "-Uw",
                             "-Broad",
                             "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_noenet.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                           "_dist",
	                           "Gm12878-",".bed", 
                             "-Haib", 
                             "-Sydh",
                             "-Uta",
                             "-Uw",
                             "-Broad",
                             "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

@@

```{r}
all_propimp_gm12878 <- data.frame(Importance=c(varimp_gm12878_5kb$aveimp5kb,
                                                   varimp_gm12878_10kb$aveimp10kb,
                                                   varimp_gm12878_25kb$aveimp25kb,
                                                   varimp_gm12878_50kb$aveimp50kb,
                                                   varimp_gm12878_100kb$aveimp100kb),
                                  Feature=c(as.character(varimp_gm12878_10kb$Feature),
                                            as.character(varimp_gm12878_10kb$Feature),
                                            as.character(varimp_gm12878_10kb$Feature),
                                            as.character(varimp_gm12878_10kb$Feature),
                                            as.character(varimp_gm12878_10kb$Feature)),
                                  Resolution=c(rep("5 kb", 78),
                                               rep("10 kb", 78),
                                               rep("25 kb", 78),
                                               rep("50 kb", 78),
                                               rep("100 kb", 78))
                                  )

@@

all_propimp_gm12878_summ <- data.frame(Prop.VI = c(#5kb
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="5 kb" & all_propimp_gm12878$Annotation=="CSS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="5 kb")]),
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="5 kb" & all_propimp_gm12878$Annotation=="HM")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="5 kb")]),
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="5 kb" & all_propimp_gm12878$Annotation=="TFBS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="5 kb")]),

                                                   #10kb
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="10 kb" & all_propimp_gm12878$Annotation=="CSS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="10 kb")]),
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="10 kb" & all_propimp_gm12878$Annotation=="HM")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="10 kb")]),
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="10 kb" & all_propimp_gm12878$Annotation=="TFBS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="10 kb")]),

@@

                                                   #100kb
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb" & all_propimp_gm12878$Annotation=="CSS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb")]),
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb" & all_propimp_gm12878$Annotation=="HM")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb")]),
                                                   sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb" & all_propimp_gm12878$Annotation=="TFBS")])/sum(all_propimp_gm12878$Importance[which(all_propimp_gm12878$Resolution=="100 kb")])),
                                       Resolution = c(rep("5 kb", 3),
                                                      rep("10 kb", 3),
                                                      rep("25 kb", 3),
                                                      rep("50 kb", 3),
                                                      rep("100 kb", 3)),
                                       Annotation = rep(c("CSS","HM","TFBS"), 5))

all_propimp_gm12878_summ$Resolution <- factor(all_propimp_gm12878_summ$Resolution, levels=c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))

@@

```{r}
annots <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/k562", pattern = "*.bed")
annots <- gsub(paste(c("K562-",".bed", 
                             "-Haib", 
                             "-Sydh",
                             "-Uta",
                             "-Uw",
                             "-Broad",
                             "-Uchicago"), collapse = "|"), "", annots)
annots <- annots[!duplicated(annots)]

chromstates <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/k562/BroadHMM")
chromstates <- chromstates[grep("K562", chromstates)]
chromstates <- gsub(paste0(c("K562-", ".bed"), collapse = "|"),"",chromstates)

histones <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/k562/HistoneModifications")
histones <- histones[grep("K562", histones)]
histones <- gsub(paste0(c("K562-", ".bed"), collapse = "|"),"",histones)

tfbs <- list.files("Z:/TAD_data_analysis/annotations/all_common_annotations/k562/TFBS")
tfbs <- gsub(paste0(c("K562-", ".bed", "-Haib", "-Sydh", "-Broad", "-Uw", "-Uta", "-Chicago"), collapse = "|"),"", tfbs)
tfbs <- tfbs[!duplicated(tfbs)]

@@

##5kb

```{r}
varimp_K562_5kb <- matrix(nrow=length(annots), ncol=21)
rownames(varimp_K562_5kb) <- annots

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_noenet.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                           "_dist",
	                           "K562-",".bed", 
                             "-Haib", 
                             "-Sydh",
                             "-Uta",
                             "-Uw",
                             "-Broad",
                             "-Uchicago"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

		varimp_K562_5kb[match(varimps$Feature,annots),i] <- varimps$Importance
}

varimp_K562_5kb <- data.frame(Feature = rownames(varimp_K562_5kb),
                                  aveimp5kb = rowMeans(varimp_K562_5kb, na.rm = TRUE),
                                  sdimp5kb = apply(varimp_K562_5kb,1, sd, na.rm = TRUE))
rownames(varimp_K562_5kb) <- NULL
```

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_noenet.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                           "_dist",
	                           "K562-",".bed", 
                             "-Haib", 
                             "-Sydh",
                             "-Uta",
                             "-Uw",
                             "-Broad",
                             "-Uchicago"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/25kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_noenet.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                           "_dist",
	                           "K562-",".bed", 
                             "-Haib", 
                             "-Sydh",
                             "-Uta",
                             "-Uw",
                             "-Broad",
                             "-Uchicago"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/50kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_noenet.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                           "_dist",
	                           "K562-",".bed", 
                             "-Haib", 
                             "-Sydh",
                             "-Uta",
                             "-Uw",
                             "-Broad",
                             "-Uchicago"), collapse = "|"), "", varimps$Feature)	
	  varimps <- varimps[order(varimps$Feature),]

@@

chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
	  varimps <- readRDS(paste0("Z:/TAD_data_analysis/K562/100kb/results_by_chr/",
									   chrs[i], 
									   "/smote/distance/enet/rfimpvars_noenet.rds"))
	  varimps$Feature <- gsub(paste0(c("`",
	                           "_dist",
	                           "K562-",".bed", 
                             "-Haib", 
                             "-Sydh",
                             "-Uta",
                             "-Uw",
                             "-Broad",
                             "-Uchicago"), collapse = "|"), "", varimps$Feature)
	  varimps <- varimps[order(varimps$Feature),]

@@

```{r}
all_propimp_K562 <- data.frame(Importance=c(varimp_K562_5kb$aveimp5kb,
                                                  varimp_K562_10kb$aveimp10kb,
                                                   varimp_K562_25kb$aveimp25kb,
                                                   varimp_K562_50kb$aveimp50kb,
                                                   varimp_K562_100kb$aveimp100kb),
                                  Feature=c(as.character(varimp_K562_10kb$Feature),
                                            as.character(varimp_K562_10kb$Feature),
                                            as.character(varimp_K562_10kb$Feature),
                                            as.character(varimp_K562_10kb$Feature),
                                            as.character(varimp_K562_10kb$Feature)),
                                  Resolution=c(rep("5 kb", 78),
                                               rep("10 kb", 78),
                                               rep("25 kb", 78),
                                               rep("50 kb", 78),
                                               rep("100 kb", 78))
                                  )

@@

all_propimp_K562_summ <- data.frame(Prop.VI = c(#5kb
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="5 kb" & all_propimp_K562$Annotation=="CSS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="5 kb")]),
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="5 kb" & all_propimp_K562$Annotation=="HM")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="5 kb")]),
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="5 kb" & all_propimp_K562$Annotation=="TFBS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="5 kb")]),

                                                   #10kb
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="10 kb" & all_propimp_K562$Annotation=="CSS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="10 kb")]),
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="10 kb" & all_propimp_K562$Annotation=="HM")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="10 kb")]),
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="10 kb" & all_propimp_K562$Annotation=="TFBS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="10 kb")]),

@@

                                                   #100kb
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb" & all_propimp_K562$Annotation=="CSS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb")]),
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb" & all_propimp_K562$Annotation=="HM")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb")]),
                                                   sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb" & all_propimp_K562$Annotation=="TFBS")])/sum(all_propimp_K562$Importance[which(all_propimp_K562$Resolution=="100 kb")])),
                                       Resolution = c(rep("5 kb", 3),
                                                      rep("10 kb", 3),
                                                      rep("25 kb", 3),
                                                      rep("50 kb", 3),
                                                      rep("100 kb", 3)),
                                       Annotation = rep(c("CSS","HM","TFBS"), 5))

all_propimp_K562_summ$Resolution <- factor(all_propimp_K562_summ$Resolution, levels=c("5 kb", "10 kb", "25 kb", "50 kb", "100 kb"))
